Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-21 manuscript/article.Rmd
fixing up down problem rerun

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBvar.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

## Figure: Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
ss_var <- ss_sim_data[20,]
p2  <- plot_ss_result1(ss_var$ss_res[[1]],
                ss_var$CB_var_gmax_s,
                ss_var$CB_var_h_s,
                ss_var$SB_var_gmax_s,
                ss_var$SB_var_h_s,
                ss_var$PB_var_gmax_s,
                ss_var$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}

@@

p_overlay <- plot_ss_result2(ss_novar$ss_res[[1]],
                             ss_var$ss_res[[1]],
                             xlims = c(-7, -1))

@@

ss_sim_data <- ss_sim_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results <- unnest(ss_sim_data, cols = c(stability_measures))

@@

To be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).

>>>>

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CBSBPB_data <- readRDS(here("simulations/sim data/ss_res_grad_CBSBPB_var.RDS"))

ss_exp_result <- CBSBPB_data
result_index <- 1

p1  <- plot_ss_result1(CBSBPB_data,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

@@

## Figure: CBSBPB Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
p2  <- plot_ss_result1(tmp2$ss_res[[1]],
                tmp2$CB_var_gmax_s,
                tmp2$CB_var_h_s,
                tmp2$SB_var_gmax_s,
                tmp2$SB_var_h_s,
                tmp2$PB_var_gmax_s,
                tmp2$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

@@

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

@@

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp2$ss_res[[1]],
                             xlims = c(-7, -1))

## Figure: CB Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
CB_data <- readRDS(here("simulations/sim data/ss_res_grad_CB_var.RDS"))
tmp3 <- CB_data[20,]

p2  <- plot_ss_result1(tmp3$ss_res[[1]],
                tmp3$CB_var_gmax_s,
                tmp3$CB_var_h_s,
                tmp3$SB_var_gmax_s,
                tmp3$SB_var_h_s,
                tmp3$PB_var_gmax_s,
                tmp3$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp3$ss_res[[1]],
                             xlims = c(-7, -1))

## Figure: SB Stable states with variation and tradeoff

```{r ss_var, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
SB_data <- readRDS(here("simulations/sim data/ss_res_grad_SB_var.RDS"))
tmp4 <- SB_data[20,]

p2  <- plot_ss_result1(tmp4$ss_res[[1]],
                tmp4$CB_var_gmax_s,
                tmp4$CB_var_h_s,
                tmp4$SB_var_gmax_s,
                tmp4$SB_var_h_s,
                tmp4$PB_var_gmax_s,
                tmp4$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p2

```{r ss_var2, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("CBSBPB var"), echo=FALSE}

p_overlay <- plot_ss_result2(tmp1$ss_res[[1]],
                             tmp4$ss_res[[1]],
                             xlims = c(-7, -1))

@@

CBSBPB_data <- CBSBPB_data %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
results <- unnest(CBSBPB_data, cols = c(stability_measures))

@@

Maybe... to be added. Need to go both ways (oxic to anoxic, and anoxic to oxic).
